---
title: "Package improvements"
author: "John Bonney"
date: "January 10, 2019"
output: html_document
---
```{r setup, include = F}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(data.table)
library(sales.taxes)
library(checkmate)
```

The end result I want is that we have
1. One function to get the data ready
2. One function to collapse the data
3. One function to residualize the data
4. Then, I'm thinking that the user can plot the data him/herself for now

### Files

`price_application` -- this file is actually pretty clean. User supplies data, the path to the treatment data, a weighting variable (weights are required), a pretax variable, posttax variable, which kind of graphs (pre or post tax), a residualization type (if any) and an outfile.
It returns one calendar time plot.

* Make weights optional

`sales_application` -- this file is also pretty clean.

### To look at
* merge_treatment

# Residualize the data

`residualize_outcome()` and `remove_time_trends()` look good right now. The only change I would make is changing the `month_dummies` argument to `season_effects` or something (the name is just a little misleading, as quarters are often used in place of months).

In fact, we pretty much already have one function to residualize the data. We do that in one step.

# Collapse the data

## Make into event study data

One big step is making event study data.

# Function changes

### `keep_best_selling_products.R`

* Changed function/file name to `select_products`
* Have function take a vector of products (instead of `products_data` and `module_name_pd`) called `products`
* Changed name of `module_name_ad` to `module_name_col`

```{r test_select_prods}
test_dt <- data.table(product_module_code = rep(1:3, each = 2),
                      prices = runif(6, 0, 1))
best_sellers <- c(1, 3)
new_dt <- select_products(all_data = test_dt,
                          module_name_col = "product_module_code",
                          products = best_sellers)

all(new_dt$product_module_code == c(1, 1, 3, 3))
```

### `combine_scanner_data.R`

* Changed `modules_data` to `modules_to_keep`
* Updated args to `keep_best_selling

**Note:** I didn't change much in this function, though it may need some changes if it is used in the future. It didn't make sense to me to edit it right now. It served a fairly specific purpose.

### `months_to_quarters.R`

Improvements that can be made:
* Allow weights to be used when averaging/summing over months
* Allow multiple variables to be inputs
* Allow different variables to be collapsed in different ways (e.g., may want to average prices but sum sales)
